Scikit-learn: machine learning without learning the machinery

### 2014-07-06 article.tex
Tentative author list and affiliations

\author{The authors}

>>>>

%\author{G. Varoquaux \and L. Buitinck \and G. Louppe \and O. Grisel \and F.
%Pedregosa \and A. Mueller}

\author[1]{G. Varoquaux\thanks{gael.varoquaux@inria.fr}}
\author[2]{L. Buitinck}
\author[3]{G. Louppe}
\author[1]{O. Grisel}
\author[1]{F. Pedregosa}
\author[4]{A. Mueller}
\affil[1]{Parietal, INRIA, Bat 145 CEA Saclay, 91191 Gif-sur-Yvette,
France}
\affil[2]{ILPS, University of Amsterdam, Science Park 904, Amsterdam, The
Netherlands}
\affil[3]{Systems and Modeling Research Unit, University of Liège
Montefiore Institute (B28), Liège, Belgium}
\affil[4]{Amazon Development Center Germany, Berlin, Germany}
